---
title: "Film Revenue Model"
output: html_notebook
---
<strong>Business understanding</strong><br>
<a href="http://blog.jdnorthcott.com/2017/11/ready-set-go.html">Project About</a><br><br>

<strong>Data understanding</strong><br>
<a href="http://blog.jdnorthcott.com/2017/11/python-scraper-brain-dump.html">Inital Brain Dump of Python</a><br>
<a href="http://blog.jdnorthcott.com/2017/11/r-brain-dump.html">Initial Brain Dump of R</a><br><br>

<strong>Data preparation</strong><br>
<a href="http://blog.jdnorthcott.com/2017/11/implementing-python-scraper.html">Python Scraping Day One</a><br>
<a href="http://blog.jdnorthcott.com/2017/12/implementing-python-scraper-day-two.html">Python Scraping Day Two</a><br>
<a href="http://blog.jdnorthcott.com/2017/12/implementing-python-scraper-day-three.html">Python Scraping Day Three</a><br><br>
Summary:

<strong>Modeling</strong><br>
Backwards fitting

Evaluation
Fit
Test Methods
Test Results

<strong>Deployment</strong><br>
Save co-efficients in Python script
People can run themselves 

Loading RMongo and linking to local database
```{r}
require(RMongo)
mg1 <- mongoDbConnect('ds4100')
dbShowCollections(mg1)
```


Building the data.frame
```{r}
films <- dbGetQuery(mg1, 'films_agg', "{'FAILED': false}") 
```

Get all Distinct MPAA values
```{r}
mpaa.distinct <- dbGetDistinct(mg1, 'films_agg', "mpaa", "{}") 
# Any non-sense values will be 0
# Go from G -> R being 1 - n
```

Write a function to remap MPAA values to a number
```{r}

```

Possible fields to be included in the model. Going to use backwards fitting to design the model
revenue
|
v
FILM SPECIFIC
weekday
day
month
budget
length
mpaa_num
director_age
avg_actor_age

ACTOR SPECIFIC 
max_actor_film_revenue
avg_actor_film_revenue
max_actor_film_votes
avg_actor_film_votes
max_actor_film_stars
avg_actor_film_stars
max_actor_film_appearances
avg_actor_film_appearances
max_actor_film_metascore
avg_actor_film_metascore

DIRECTOR SPECIFIC
director_number_of_films
max_director_film_revenue
avg_director_film_revenue
max_director_film_votes
avg_director_film_votes
max_director_film_stars
avg_director_film_stars
max_director_film_metascore
avg_director_film_metascore


```{r}

```

Divide data into training and test
Using a random 50/50 and 30/70 split
```{r}

```

Building the two test models
```{r}

```

Running the tests
```{r}

```

Checking % correct of both model tests
```{r}

```

